method

### 2021-08-27 06_Paper/ER-ED/method.Rmd
described experimental procedure

The study consisted of two sessions, one week apart. 
Both sessions took place in a shielded cabin with constant lighting. 
Before each session, participants received information about the respective experimental procedure and signed informed consent. 
At the beginning of the first session participants filled out a demographic questionnaire. 
Afterwards the completed an n-Back task with the levels one to four.

@@

```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))

stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))
```
## 2.4. Stimuli

>>>>

The study consisted of two sessions, one week apart. 
Both sessions took place in a shielded cabin with constant lighting. 
Before each session, participants received information about the respective experimental procedure and signed informed consent. 
At the beginning of the first session participants filled out a demographic questionnaire. 
Afterwards the completed an n-Back task with the levels one to four.
Then, they completed an ED procedure on screen, followed by a random repetition of one n-back level.
The second session, containing the ER paradigm, took place exactly one week after session one.
Participants gave signed informed consent for the second session.
Afterwards the ER paradigm was conducted.
Participants first received written instructions on the ER paradigm and ER strategies that they should apply.
A training session was performed to ensure that all participants were able to implement the ER strategies.
Next, electrodes to measure EMG were attached and the ER paradigm was conducted. 
Two days after the secon sessoin, participants received a link to an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.

@@

## 2.4. Stimuli
```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))

stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))
```
